### 2014-10-09 writing/AAAI SSS '15/abstract.tex
Editing

\begin{abstract}
  Natural logic offers a powerful relational conception of meaning
  that fits well with recent distributed approaches to semantic
  representation. Such representations have proven valuable in a wide
  range of sophisticated language tasks, but it remains an open
  question whether it is possible to train them to support the rich,
  diverse logical reasoning captured by natural logic. We address this
  question for two classes of neural model: plain neural networks and
  neural tensor networks.  Our first experiment evaluates these
  models' ability to learn the basic algebra of natural logic
  relations from simulated data, and our second experiment evaluates
  them on the WordNet noun graph.  We find that the plain RNN achieves
  only mixed results, whereas the stronger NTN generalizes well in
  both settings and appears capable of learning suitable
  representations for natural language logical inference.
\end{abstract}

>>>>

\begin{abstract}
  Natural logic offers a powerful relational conception of meaning
  that is a natural counterpart to distributed semantic
  representations, which have proven valuable in a wide range of
  sophisticated language tasks. However, it remains an open question
  whether it is possible to train distributed representations to
  support the rich, diverse logical reasoning captured by natural
  logic. We address this question for two classes of neural model:
  plain neural networks and neural tensor networks (NTNs).  Our
  experiments evaluate these models' ability to learn the basic
  algebra of natural logic relations from simulated data and from the
  WordNet noun graph.  We find that the plain RNN achieves only mixed
  results, whereas the stronger NTN generalizes well in both settings
  and appears capable of learning suitable representations for natural
  language logical inference.
\end{abstract}

### 2014-10-09 writing/AAAI SSS '15/intro.tex
Editing

These approaches are naturally paired with theories using distributed
(e.g., vector) representations, where meaning is also naturally
modeled as relational. Distributed representations have been used
successfully in a wide array of sophisticated language tasks,
including sentiment analysis, analogy completion, relation extraction,
and named entity recognition. However, it remains an open question
whether it is possible to train such representations to support the
rich, diverse logical reasoning captured by natural logic; while such
representations excel at synonymy (similarity), the results are more
mixed for entailment, contradiction, and mutual consistency.

Using the natural logic of \cite{maccartney2009extended} as our formal
model, we address this open question for two classes of neural model:
plain neural networks and neural tensor networks (NTNs;
\cite{socher2013acl1}). The natural logic is built from the seven
relations defined in Table~\ref{b-table}. Its formal properties and
inferential strength of the natural logic are now well-understood
\cite{Icard:Moss:2013,Icard:Moss:2013:LILT}, so it provides a rigorous
and challenging set of goals for our distributed representations. To
keep the discussion managable, we limit attention to experiments
involving the lexicon; for a more extended treatment involving complex
expressions involving logical connectives and quantifiers, see
\cite{Bowman:Potts:Manning:2014}.

In our first experiment, we use the pre-specified logical grammar to
generate controlled data sets and assses the ability of the two
classes of neural network to learn the core underlying relational
algebra from this simulated data. In our second experiment, we define
a simple modification of the logical grammar so that it aligns well
with the WordNet noun graph, and we again assess our two classes of
RNN on this data. The controlled data of our first experiment helps us
to achieve analytic insights into what the models are able to learn,
and the large, diverse lexicon of the second experiment shows us how
they fare in the real world. We find that the plain RNN achieves only
mixed results in these experiments, whereas the stronger RNTN model
generalizes well in both cases, suggesting that it has in fact
learned, or at least learned to simulate, our target logical concepts.
% These experiments differentiate the increased power of RNTNs better
% than previous work and provide the most convincing demonstration to
% date of the ability of neural networks to model semantic inferences
% in complex natural language sentences.

>>>>

Natural logic aligns well with distributed (e.g., vector)
representations, which also naturally model meaning relationally.
Distributed representations have been used successfully in a wide
array of sophisticated language tasks. %,
% including sentiment analysis, analogy completion, relation
% extraction, and named entity recognition.
However, it remains an open question whether it is possible to train
such representations to support the rich, diverse logical reasoning
captured by natural logic; while they excel at
synonymy (similarity), the results are more mixed for entailment,
contradiction, and mutual consistency.  Using the natural logic of
\cite{maccartney2009extended} as our formal model, we address this
open question for two classes of neural model: plain neural networks
and neural tensor networks (NTNs; \cite{socher2013acl1}). The natural
logic is built from the seven relations defined in
Table~\ref{b-table}. Its formal properties are now well-understood
\cite{Icard:Moss:2013,Icard:Moss:2013:LILT}, so it provides a rigorous
set of goals for our neural models. To keep the discussion managable,
we limit attention to experiments involving the lexicon; for a more
extended treatment of complex expressions involving logical
connectives and quantifiers, see \citet{Bowman:Potts:Manning:2014}.

In our experiments, we evaluate these models' ability to learn the
basic algebra of natural logic relations from simulated data and from
the WordNet noun graph. The simulated data help us to achieve analytic
insights into what the models learn, and WordNet data show how they
fare in the real world.  We find that the plain RNN achieves only
mixed results in these experiments, whereas the stronger RNTN model
generalizes well in both cases, suggesting that it has in fact
learned, or at least learned to simulate, our target logical concepts.

% In our first experiment, we use the pre-specified logical grammar to
% generate controlled data sets and assess the ability of the two
% classes of neural network to learn the core underlying relational
% algebra from this simulated data. In our second experiment, we define
% a simple modification of the logical grammar so that it aligns with
% the WordNet noun graph, and we again assess our two classes of RNN on
% this data. The controlled data of our first experiment helps us to
% achieve analytic insights into what the models are able to learn, and
% the large, diverse lexicon of the second experiment shows us how they
% fare in the real world.

% These experiments differentiate the increased power of RNTNs better
% than previous work and provide the most convincing demonstration to
% date of the ability of neural networks to model semantic inferences
% in complex natural language sentences.

### 2014-10-09 writing/AAAI SSS '15/methods.tex
Editing

We follow the approach to learning semantically meaningful embeddings 
of \citet{Bowman:Potts:Manning:2014}, which is centered on the problem of
labeling a pair of words or sentences with one of a small set of logical
relations. The architecture of the model that we use, which is limited
to only pairs of single symbols (such as words), is depicted in
Figure~\ref{sample-figure}. The model represents the two input symbols
as embeddings, which are fed into a comparison function based on one
of two types of neural network layer functions to produce a representation
for the relationship between the two symbols. This representation is then
fed into a simple softmax classifier which outputs a distribution over
possible labels. The entire network, including the embeddings, are trained
through backpropagation with AdaGrad \cite{duchi2011adaptive}.

>>>>

We follow the approach to learning semantically meaningful embeddings 
of \cite{Bowman:Potts:Manning:2014}, which is centered on the problem of
labeling a pair of words or sentences with one of a small set of logical
relations. The architecture of the model that we use, which is limited
to only pairs of single symbols (such as words), is depicted in
Figure~\ref{sample-figure}. The model represents the two input symbols
as embeddings, which are fed into a comparison function based on one
of two types of neural network layer functions to produce a representation
for the relationship between the two symbols. This representation is then
fed into a simple softmax classifier which outputs a distribution over
possible labels. The entire network, including the embeddings, are trained
through backpropagation with AdaGrad \cite{duchi2011adaptive}.
